Exploring the Usefulness of Varactor loaded Nonlinear Transmission Lines

### 2020-06-03 RohdeAndSchwarzWhitePaper/Draft_White_Paper.tex
Updated Report and picture filenames
Moved image directories for easier access
Added more image edits

% *** GRAPHICS RELATED PACKAGES ***
%
%\ifCLASSINFOpdf
  \usepackage{graphicx}
  % declare the path(s) where your graphic files are
\graphicspath{{./images/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % declare the path(s) where your graphic files are
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

Figure \ref{fig:ACResp56nh} shows the simulated AC response of our 10 ladder long circuit.

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth,page = 1]{ACResponseB1.png}
\caption{\ AC Response of Board 1 (L = 56nH) 
}\label{fig:ACResp56nh}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth,page={1}]{Probed_Input_N10_N240_NoSeriesResistance.pdf}
\caption{\
}\label{fig:ProbedTransientNoSer}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{Board1/MeasuredACResponseB1.BMP}
\caption{}
\label{}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{}
\caption{}
\label{}
\end{figure}

@@

Before grappling with these issues, we were able to measure this pulse sharpening effect using a higher bandwidth oscilloscope as shown in figure \ref{fig:FirstRandS}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{Risetime_RandS}
\caption{Risetime can be seen to be reduced by our transmission line}
\label{fig:FirstRandS}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{}
\caption{}
\label{}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{}
\caption{}
\label{}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{}
\caption{}
\label{}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth,page = 1]{images/MostRecentSparamMeasSchem.pdf}
\caption{\ Schematic used to generate S-parameter plots  
}\label{fig:sparamSchem}
\end{figure}

@@

\

>>>>

% *** GRAPHICS RELATED PACKAGES ***
%
%\ifCLASSINFOpdf
  \usepackage{graphicx}
  % declare the path(s) where your graphic files are
\graphicspath{{./images/}{./images/Board1/}{./images/Board2/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % declare the path(s) where your graphic files are
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
%  \DeclareGraphicsExtensions{.bmp}
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth,page={1}]{Probed_Input_N10_N240_NoSeriesResistance.pdf}
\caption{\ Comparing Risetime in Simulations at Input node Node 10 and Node 240
}\label{fig:ProbedTransientNoSer}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{MeasuredACResponseB1.png}
\caption{Measured Frequency Response for Board 1 (L= 56nH)}
\label{fig:MeasACBoard1}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{ACResponseB1}
\caption{Simulated AC Response for Board 1}
\label{fig:simACBoard1}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{MeasuredACResponseB2.png}
\caption{Measured Frequency Response for Board 2 (L= 560nH)}
\label{fig:MeasACBoard2}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{ACResponseB1}
\caption{Simulated AC Response for Board L=560nH}
\label{fig:simACBoard2}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth,angle = -90]{SetupWithBiasing.JPG}
\caption{Test Setup for Measuring Risetime With Bias}
\label{fig:SetupWBiasing}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{Probed_Input_N10_N240_NoSeriesResistance}
\caption{Simulated Risetimes for Input pulse, $10^{th}$ node, and the $240^{th}$ node}
\label{fig:probedNoResistance}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{Probed_Input_N10_N240_NoSeriesResistance}
\caption{Accounting for Series Resistance shows that there is a certain point where no more sharpening takes place}
\label{fig:probedWithResistance}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{MeasuredSquareResponseB1.png}
\caption{Risetime Measurement from Board 1 (L=56nH)}
\label{fig:MeasuredSquareGeneric}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{MeasuredSquare1VBiasB1.png}
\caption{}
\label{fig:MeasuredSquare1VBiasB1}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{MeasuredSquare2VBiasB1.png}
\caption{}
\label{fig:Measured Risetime with 2V DC Bias}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth,page = 1]{images/MostRecentSparamMeasSchem.pdf}
\caption{Schematic used to generate S-parameter plots. The top line measures S11 and S12, and bottom line measures S21 and S22. 
}\label{fig:sparamSchem}
\end{figure}

@@
